Evolutionary rescue and reintroduction of resistant frogs allows recovery in the presence of a lethal fungal disease

### 2023-12-03 doc/manuscript/translocation.qmd

We estimated survival and recruitment for each site using open population mark recapture models based on @joseph2018.
For each individual $i=1, ..., M$ on each survey $j=1, ..., n_j$: $o_{i, j} = 1$ if the individual was not detected, and $o_{i, j}=2$ if the individual was detected. 
Capture histories of $M$ individuals are modeled, though only $N_s$ individuals were captured.
This parameter expanded data augmentation allows us to capture the possibility that undetected individuals may have recruited into the adult population [@royle2012parameter]. 
Here, $M$ was chosen to be three times the number of observed individuals ($3N_s$) to be considerably greater than our prior guess of $N_s$.

We denote the true state of individual $i$ as $u_{i, t}$ for primary period $t = 1,..., n_t$. 
The four states that we consider are: $u_{i, t} = 1$ for individuals that have not recruited, $u_{i, t} =2$ for live adults, and $u_{i, t} = 3$ for dead adults. 
Each survey $j=1, ..., n_j$ occurs in one of the $n_t$ primary periods, and we denote the primary period in which survey $j$ takes place as $t_j$. 
Each primary period $t$ occurs within one year, but within a year there are multiple primary periods.
We set the year containing the first primary period to $y_{t = 1} = 1$, and generally $y_t$ represents the year containing primary period $t$. 
Years increment by one until the final year of the mark recapture efforts, which we denote $n_y$: $y \in \{1, 2, ..., n_y\}$.
We assume that within a primary period, the state of each individual does not change (i.e., individuals do not recruit into the adult population, gain or lose Bd infection, or die). 
This assumption is justified by the short time intervals between surveys within primary periods.

@@

We computed the likelihood of each individual capture history using the forward algorithm, and we estimated the latent states using the forward-backward algorithm [@zucchini2009hidden, @joseph2018]. 
All of the code to specify and fit the model in Stan is available in the open source mrmr package [@joseph2019].

>>>>

We estimated survival and recruitment for each site using open population mark recapture models based on @joseph2018.
For each individual $i=1, ..., M$ on each survey $j=1, ..., n_j$: $o_{i, j} = 1$ if the individual was not detected, and $o_{i, j}=2$ if the individual was detected.
Capture histories of $M$ individuals are modeled, though only $N_s$ individuals were captured.

This parameter expanded data augmentation allows us to capture the possibility that undetected individuals may have recruited into the adult population [@royle2012]. 
Here, $M$ was chosen to be three times the number of observed individuals ($3N_s$) to be considerably greater than our prior guess of $N_s$.

We denote the true state of individual $i$ as $u_{i, t}$ for primary period $t = 1,..., n_t$. 
The four states that we consider are: $u_{i, t} = 1$ for individuals that have not recruited, $u_{i, t} =2$ for live adults, and $u_{i, t} = 3$ for dead adults. 
Each survey $j=1, ..., n_j$ occurs in one of the $n_t$ primary periods, and we denote the primary period in which survey $j$ takes place as $t_j$. 
Each primary period $t$ occurs within one year, but within a year there can be multiple primary periods.
We set the year containing the first primary period to $y_{t = 1} = 1$, and generally $y_t$ represents the year containing primary period $t$. 
Years increment by one until the final year of the mark recapture efforts, which we denote $n_y$: $y \in \{1, 2, ..., n_y\}$.
We assume that within a primary period, the state of each individual does not change (i.e., individuals do not recruit into the adult population, gain or lose Bd infection, or die). 
This assumption is justified by the short time intervals between surveys within primary periods, in cases where primary periods contain multiple secondary periods.

@@

We computed the likelihood of each individual capture history using the forward algorithm, and we estimated the latent states using the forward-backward algorithm [@zucchini2009, @joseph2018].

All of the code to specify and fit the model in Stan is available in the open source mrmr package [@joseph2019].
